### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Explanatory Variables

I divide women into three groups based on education attainment: no
education, 1 to 7 years of education, and 8 and more years of education.
The models are estimated separately for each education level to reduce
the potential problem of including other variables as proportional.
Increasing education of mothers correlates closely with lower fertility 
\citep{schultz97}, and 
we should expect lower fertility to lead to more use of sex selection.%
\footnote{
Fathers' education has two opposite predicted effects: the associated higher income
should increase fertility and therefore lower the pressure to use sex selection, but
the higher income also makes the use of sex selection cheaper.
In practice, fathers' education had little effect on the hazards and the use of 
sex-selective abortions, and I, therefore, do not include it.
}

@@

The area of residence is a dummy variable for the household living in
an urban area.
The cost of children is higher in urban areas than in rural areas, and 
there is easier access to prenatal sex determination in urban areas.
Both factors are likely to lead to higher use of sex-selective abortions
in urban than in rural areas.

The second group of variables consists of those expected to have an 
approximately proportional effect on the hazard.
These include the length of the first spell 
(for the second and higher-order spells to capture fecundity), 
the age of the mother at the beginning of the spell, 
whether the household owns any land, 
and whether the household belongs to a scheduled tribe or caste.
We cannot observe fecundity directly, but the time from marriage until 
first birth is a suitable proxy because most Indian women do not use 
contraception before the first birth and there is pressure to show that 
a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
This is confirmed below by the very short spells between marriage and first birth,
even among the most educated.
Hence, a long spell between marriage and first birth is likely due to low fecundity.
For both duration from marriage to first birth and the age of the mother at the 
beginning of the spell, I also include their squares.
The remaining variables are dummies for household ownership of land and membership
of a scheduled caste or tribe.

>>>>

I divide women into three groups based on education attainment: no
education, one to seven years of education, and eight and more years of education.
The models are estimated separately for each education level to reduce
the potential problem of including other variables as proportional.
Increasing education of mothers correlates closely with lower fertility 
\citep{schultz97}, and 
we should expect lower fertility to lead to more use of sex selection.%
\footnote{
Fathers' education has two opposite predicted effects: the associated higher income
should increase fertility and therefore lower the pressure to use sex selection, but
the higher income also makes the use of sex selection cheaper.
In practice, fathers' education had little effect on the hazards and the use of 
sex-selective abortions, and I, therefore, do not include it.
}

@@

Area of residence is a dummy variable for the household living in
an urban area.
The cost of children is higher in urban areas than in rural areas, and 
there is easier access to prenatal sex determination in urban areas.
Both factors are likely to lead to higher use of sex-selective abortions
in urban than in rural areas.

The second group of variables consists of those expected to have an 
approximately proportional effect on the hazard.
These include the length of the first spell 
(for the second and higher-order spells to capture fecundity), 
the age of the mother at the beginning of the spell, 
whether the household owns any land, 
and whether the household belongs to a scheduled tribe or caste.
We cannot observe fecundity directly, but the time from marriage until 
first birth is a suitable proxy because most Indian women do not use 
contraception before the first birth and there is pressure to show that 
a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
The absence of contraception before the first birth is confirmed below by the 
very short spells between marriage and first birth, even among the most educated.
Hence, a long spell between marriage and first birth is likely due to low fecundity.
For both duration from marriage to first birth and the age of the mother at the 
beginning of the spell, I also include their squares.
The remaining variables are dummies for household ownership of land and membership
of a scheduled caste or tribe.
